Modelling last glacial cycle ice dynamics in the Alps

### 2018-07-20 articles/cycle/response-referee1.tex

    In the review paper by \citet{Heiri.etal.2014}, the latter has been
    specifically identified as a neeeded future development, but to our
    knowledge, no quantitative reconstruction has been made available since
    then. The following word of caution was also added in the conclusions:

    \msquote{%
        This suprising result is likely coincidental as there is no direct link
        between European and Antarctic climate. This highlights the need for
        more quantitative reconstructions of European palaeoclimate.}

    \referee{%
        A PDD scheme is used based only on seasonal air temperatures. van de
        Berg et al. (Nature Geosc., 2011) showed that for long-term variations
        including the Eemian, orbital changes in insolation are important and
        should be considered explicitly. This could be particularly relevant
        here, because the EPICA core does not reflect changes in insolation
        over the Alps. In further work, an insolation-change term (summer,
        local) could be combined with EPICA in the climate temperature
        paleo-forcing.}

    We agree. This is one of many possible improvements that could be tested
    upon the climate forcing used here. In the conclusions we now advocate for:

    \msquote{%
        a more realistic climate forcing based on regional circulation model
        output or including the effect of long-term term changes in incoming
        solar radiation.}

### 2018-07-20 articles/cycle/alps-cycle.tex
Assess referee 1 comment on insulation.

    More importantly, these results are limited by the simplicity of the
    surface mass balance parameters and climate forcing used.
    In particular, additional palaeo-climate variability over
    the European Alps may have caused more glaciations than modelled here.
    Using more specifically targeted sensitivity runs, future
    modelling studies will certainly be able to quantify uncertainties
    associated with some of the above limitations. Nevertheless, we hope that
    these conclusions will also serve as a basis for future studies of glacial
    geology in the Alps, and call for a more systematic aggregation and
    homogenization of glacial geological data to form a basis for model
    validation across the entire Alpine range.

>>>>

    More importantly, these results are limited by the simplicity of the
    surface mass balance parameters and climate forcing used.
    In particular, additional palaeo-climate variability over
    the European Alps may have caused more glaciations than modelled here.
    Using more specifically targeted sensitivity runs, and a more realistic
    climate forcing based on regional circulation model output or including
    the effect of long-term term changes in incoming solar radiation, future
    modelling studies will certainly be able to quantify uncertainties
    associated with some of the above limitations. Nevertheless, we hope that
    these conclusions will also serve as a basis for future studies of glacial
    geology in the Alps, and call for a more systematic aggregation and
    homogenization of glacial geological data to form a basis for model
    validation across the entire Alpine range.
